Preprocessing_&_Plot_for_Moral_Categ_Replication

### 2018-06-26 Replication/Results/data_analysis/preproc/Analysis_exp7_prepro.rmd

# do the same to data from categorization, get the raw data for categorization task
fNames.c <- list.files(path = rawDir, pattern = "data_exp7_rep_categ_*")
fNames.c <- paste(rawDir,fNames.c, sep = '')
df.T    <- do.call("rbind",lapply(as.list(fNames.c),FUN=function(files){read.table(files, header=TRUE, sep="",stringsAsFactors=F)}))

>>>>

# do the same to data from categorization, get the raw data for categorization task
fNames.c <- list.files(path = rawDir, pattern = "data_exp7_rep_categ_*")
# remove invalid data data_exp7_rep_categ_7338.out
fNames.c <- fNames.c[fNames.c != "data_exp7_rep_categ_7338.out"]
fNames.c <- paste(rawDir,fNames.c, sep = '')
df.T    <- do.call("rbind",lapply(as.list(fNames.c),FUN=function(files){read.table(files, header=TRUE, sep="",stringsAsFactors=F)}))
